---
output:
  bookdown::pdf_document2: 
    keep_tex: true
    toc: false
 # bookdown::html_document2: default
 # keep_tex: yes
 
---

```{r, include=FALSE}
library(emmeans)
library(here)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                       dev=c("png"),
                     # fig.width = 8, fig.height = 8, 
                      fig.pos = "H", table.placement = "H")
library(tidyverse)
library(dplyr)
library(magrittr)
library(MASS)
library(ggpmisc) # for function stat_poly_eq
library(broom) # for function tidy
library(nlme) #for function gls
library(kableExtra)
source("functions.R")
library(fabricatr)  #for function split_quantile
options(digits = 6) #to accommodate very small values
set.seed(505) #to make sure the prediction equation R2 come out the same when others run this file 
```

```{r, include=FALSE}
## Read in the individual dried aboveground mass and fecundity 

fecundity18 <- read_csv(here("2-Data/Clean/fecundity_18.csv"), 
    col_types = cols(Biomass = col_number(), 
        Seed = col_number()), na = "empty")

fecundity18$Crop_ID <- factor(fecundity18$Crop_ID, 
                              levels = c("C2", "S2",
                                         "C3", "S3", "O3",
                                         "C4", "S4", "O4", "A4"))

# Make sure that Block, Crop ID, Corn_weed_management, and bt are factors
fecundity18  <- fecundity18   %<>%
  mutate_at(c("Block","Crop_ID","Corn_weed_management", "bt"),funs(factor(.)))

# Look at the geometric means of number of seeds 
fecundity18_avg <- fecundity18%>%
  group_by(Plot,Side)%>%
  mutate(m_Seed = mean(log(Seed+1)))%>%
  slice(1)

```

## Individual female aboveground mass and fecundity {-}

```{r, include=FALSE}
## Keep complete cases only (390/391 entries)
fecundity18_b <- fecundity18[complete.cases(fecundity18$Biomass), ]
# min(fecundity18_b$Biomass[fecundity18_b$Biomass > 0])

biomass.gls <- gls(log(Biomass + 0.005) ~ Block + 
                     Crop_ID*Corn_weed_management,
  correlation=corCompSymm(form= ~1 | bt), #identifies each treatment within block
  data=fecundity18_b)

## Keep complete cases only (390/391 entries)
fecundity18_s <- fecundity18[complete.cases(fecundity18$Seed), ]
min(fecundity18_s$Seed[fecundity18_s$Seed > 0])

seeds.gls <- gls(log(Seed + 1) ~ Block + 
                   Crop_ID*Corn_weed_management,
  correlation=corCompSymm(form= ~1 | bt), #identifies each treatment within block
  data=fecundity18_s)


biomass.gls_jt <- joint_tests(emmeans(biomass.gls, c("Crop_ID", "Corn_weed_management"))) 
biomass.gls_jt$`model term` <- gsub(":", " x ", biomass.gls_jt$`model term`)
biomass.gls_jt$`model term` <- gsub("_", " ", biomass.gls_jt$`model term`)
biomass.gls_df <- print(biomass.gls_jt, export = TRUE)


seeds.gls_jt <- joint_tests(emmeans(seeds.gls, c("Crop_ID", "Corn_weed_management"))) 
seeds.gls_jt$`model term` <- gsub(":", " x ", seeds.gls_jt$`model term`)
seeds.gls_jt$`model term` <- gsub("_", " ", seeds.gls_jt$`model term`)

seeds.gls_df <- print(seeds.gls_jt, export = TRUE)

biom_seed_gls <- cbind(biomass.gls_df$summary,seeds.gls_df$summary)

rownames(biom_seed_gls) <- NULL
```

```{r, include=FALSE}
## Add Crop as a new factoring item to use in the next 2 chunks 
Crop <- factor(c("corn", "soybean",
                 "corn", "soybean", "oat", 
                 "corn", "soybean", "oat", "alfalfa"),
                     levels = c("soybean", "corn",  "oat", "alfalfa"))

```



```{r, include=FALSE}
## Rotation effect on individual biomass, assessed within the same crop species
indiv_biom_corn <-  emmeans(biomass.gls,
                            ~ Crop_ID | Corn_weed_management, 
                            infer = c(FALSE,TRUE), 
                            type = "response", 
                            at = list(Crop_ID = c("C2", "C3", "C4")))

indiv_biom_corn_ct <- contrast(indiv_biom_corn, 
                               "pairwise", 
                               type = "response",
                               infer = c(FALSE,TRUE)) %>% 
  print(export = TRUE)

indiv_biom_soy <- emmeans(biomass.gls,
                          c("Crop_ID", "Corn_weed_management"),
                          infer = c(FALSE,TRUE), 
                          type = "response",
                          at = list(Crop_ID = c("S2", "S3", "S4"))) 

indiv_biom_soy_ct <- contrast(indiv_biom_soy,
                              by = "Corn_weed_management" ,"pairwise",
                              type = "response",
                              infer = c(FALSE,TRUE)) %>%
  print(export = TRUE)

indiv_biom_oat <- emmeans(biomass.gls,
                          ~ Crop_ID| Corn_weed_management,
                          infer = c(FALSE,TRUE), 
                          type = "response",
                          at = list(Crop_ID = c("O3", "O4")))

indiv_biom_oat_ct <- contrast(indiv_biom_oat,
                              "pairwise",
                              type = "response",
                              infer = c(FALSE,TRUE)) %>% 
  print(export = TRUE)

indiv_biom_grid <- ref_grid(biomass.gls)

indiv_biom_grid_crop <- add_grouping(indiv_biom_grid , "Crop", "Crop_ID", Crop)

## Crop species effect on individual biomass
# crop contrast, averaged over rotations
indiv_biom_crop <- emmeans(indiv_biom_grid_crop , 
                           ~ Crop | Corn_weed_management,
                         infer = c(FALSE,TRUE),  type = "response") 

indiv_biom_crop_ct <- contrast(indiv_biom_crop , 
                             "pairwise", 
                             type = "response",
                             infer = c(FALSE,TRUE)) %>%
  print(export = TRUE)


indiv_biom_ct_conv <- rbind(indiv_biom_corn_ct$summary$`Corn_weed_management = conv`,
                        indiv_biom_soy_ct$summary$`Corn_weed_management = conv`,
                        indiv_biom_oat_ct$summary$`Corn_weed_management = conv`,
                   indiv_biom_crop_ct$summary$`Corn_weed_management = conv`)

indiv_biom_ct_conv_df <- as.data.frame(indiv_biom_ct_conv)

indiv_biom_ct_conv_df[,c(2:6)] <- sapply(indiv_biom_ct_conv_df[,c(2:6)],as.numeric)

indiv_biom_ct_conv_rounded <- indiv_biom_ct_conv_df %>%
  mutate(across(where(is.numeric), ~ as.numeric(sprintf('%.2f', .)))) %>%
#  mutate(across(where(is.numeric), as.character)) %>% #remove trailing zeros
  as_tibble # prevent adding trailing zeros later



indiv_biom_ct_low <- rbind(indiv_biom_corn_ct$summary$`Corn_weed_management = low`,
                        indiv_biom_soy_ct$summary$`Corn_weed_management = low`,
                        indiv_biom_oat_ct$summary$`Corn_weed_management = low`,
                   indiv_biom_crop_ct$summary$`Corn_weed_management = low`)

indiv_biom_ct_low_df <- as.data.frame(indiv_biom_ct_low)

indiv_biom_ct_low_df[,c(2:6)] <- sapply(indiv_biom_ct_low_df[,c(2:6)],as.numeric)

indiv_biom_ct_low_rounded <- indiv_biom_ct_low_df %>%
  mutate(across(where(is.numeric), ~ as.numeric(sprintf('%.2f', .)))) %>%
#  mutate(across(where(is.numeric), as.character)) %>% #remove trailing zeros
  as_tibble # prevent trailing zeros later


## Merge conventional (left) with low corn weed management (right) for individual biomass 
indiv_biom_ct <- cbind(indiv_biom_ct_conv_rounded[,-c(3:6)], indiv_biom_ct_low_rounded[,-c(3:6)])
         
row.names(indiv_biom_ct) <- NULL

```


```{r, include=FALSE}
## Rotation effect on individual fecundity, assessed within the same crop species
indiv_seeds_corn <-  emmeans(seeds.gls,
                             ~ Crop_ID | Corn_weed_management,
                             infer = c(FALSE,TRUE),
                             type = "response",
                             at = list(Crop_ID = c( "C2", "C3", "C4")))

indiv_seeds_corn_ct <- contrast(indiv_seeds_corn,
                                "pairwise",
                                type = "response",
                                infer = c(FALSE,TRUE)) %>%
  print(export = TRUE)

indiv_seeds_soy <- emmeans(seeds.gls,
                           c("Crop_ID", "Corn_weed_management"), 
                           infer = c(FALSE,TRUE),
                           type = "response", 
                           at = list(Crop_ID = c("S2", "S3", "S4"))) 

indiv_seeds_soy_ct <- contrast(indiv_seeds_soy,
                               by = "Corn_weed_management" ,"pairwise",
                               type = "response", infer = c(FALSE,TRUE)) %>% print(export = TRUE)

indiv_seeds_oat <- emmeans(seeds.gls,
                           ~ Crop_ID| Corn_weed_management,
                           infer = c(FALSE,TRUE), 
                           type = "response",
                           at = list(Crop_ID = c("O3", "O4")))

indiv_seeds_oat_ct <- contrast(indiv_seeds_oat ,
                               "pairwise",
                               type = "response",
                               infer = c(FALSE,TRUE)) %>%
  print(export = TRUE)


## Crop species effect on individual fecundity 
# crop contrast, averaged over rotations
indiv_seeds_grid <- ref_grid(seeds.gls)
indiv_seeds_grid_crop <- add_grouping(indiv_seeds_grid , "Crop", "Crop_ID", Crop)
indiv_seeds_crop <- emmeans(indiv_seeds_grid_crop ,
                            ~ Crop | Corn_weed_management,
                            infer = c(FALSE,TRUE), 
                            type = "response") 
indiv_seeds_crop_ct <- contrast(indiv_seeds_crop ,
                                "pairwise", 
                                type = "response",
                                infer = c(FALSE,TRUE)) %>% 
  print(export = TRUE)


#### customized contrasts, Corn_weed_management NS  with indiv_seeds_emm ###

##Impact of crop species and rotation on individual fecundity: conventional corn weed management
indiv_seeds_ct_conv <- rbind(indiv_seeds_corn_ct$summary$`Corn_weed_management = conv`,
                         indiv_seeds_soy_ct$summary$`Corn_weed_management = conv`,
                         indiv_seeds_oat_ct$summary$`Corn_weed_management = conv`,
                   indiv_seeds_crop_ct$summary$`Corn_weed_management = conv`)

indiv_seeds_ct_conv_df <- as.data.frame(indiv_seeds_ct_conv)

indiv_seeds_ct_conv_df[,c(2:6)] <- sapply(indiv_seeds_ct_conv_df[,c(2:6)],as.numeric)

indiv_seeds_ct_conv_rounded <- indiv_seeds_ct_conv_df %>%
  mutate(across(where(is.numeric), ~ as.numeric(sprintf('%.2f', .)))) %>%
#  mutate(across(where(is.numeric), as.character)) %>% #remove trailing zeros
  as_tibble # prevent adding trailing zeros later

##Impact of crop species and rotation on individual fecundity: low herbicide corn weed management
indiv_seeds_ct_low <- rbind(indiv_seeds_corn_ct$summary$`Corn_weed_management = low`,
                         indiv_seeds_soy_ct$summary$`Corn_weed_management = low`,
                         indiv_seeds_oat_ct$summary$`Corn_weed_management = low`,
                   indiv_seeds_crop_ct$summary$`Corn_weed_management = low`)

indiv_seeds_ct_low_df <- as.data.frame(indiv_seeds_ct_low)

indiv_seeds_ct_low_df[,c(2:6)] <- sapply(indiv_seeds_ct_low_df[,c(2:6)],as.numeric)

indiv_seeds_ct_low_rounded <- indiv_seeds_ct_low_df %>%
  mutate(across(where(is.numeric), ~ as.numeric(sprintf('%.2f', .)))) %>%
#  mutate(across(where(is.numeric), as.character)) %>% #remove trailing zeros
  as_tibble # prevent adding trailing zeros later

### Merge conventional (left) with low corn weed management (right) for individual fecundity 

indiv_seeds_ct <- cbind(indiv_seeds_ct_conv_rounded[,-c(3:6)], indiv_seeds_ct_low_rounded[,-c(3:6)])
         
row.names(indiv_seeds_ct) <- NULL
```

Individual female aboveground mass and fecundity were affected by rotation, crop species, and corn weed management (Table \@ref(tab:indiv-biom-fecund-ct)). Crop identity was more influential on female aboveground mass and fecundity than corn weed management regime, but the effect of crop identity differed between corn weed management regimes (Table \@ref(tab:ancova-jt)A and \@ref(tab:ancova-jt)B). Differences in relative female size and fecundity across rotation by herbicide treatments were attributed to the relative size and fecundity differences when the waterhemp populations grew in different crops' presence.  

Individual female aboveground mass was comparable in most pairwise comparison of the same crop species in different rotations, except S2 versus S3 (p-value = 0.0076) and S3 versus S4 (p-value = 0.0268) that followed corn under conventional weed management and C2 versus C3 (p-value = 0.0064) under low weed management. Averaged over rotations, individual female aboveground mass was 3.5- to 133.6-fold different across each pair of comparison (p-values < 0.05), except for corn under low weed management versus the succeeding oat (p-value = 0.9616).  

Individual fecundity was comparable in most pairwise comparison of the same crop species in different rotations, except S2 versus S3 (p-value = 0.001) and S3 versus S4 (p-value = 0.0046) that followed corn under conventional weed management and C2 versus C3 under low weed management (p-value = 0.0032), and O3 versus O4 that followed corn under low weed management (p-value = 0.0321). Averaged over rotations, individual fecundity was comparable between corn under low herbicide and oat in the same system (p-value = 0.4904) but was 6.3- to 6857.1-fold different in other pairs of comparison (p-values $\leq$ 0.0001). 

```{r indiv-biom-fecund-ct, echo=FALSE}

# Merge individual biomass (left) with individual fecundity (right), side by side
indiv_biom_seeds_ct <- cbind(indiv_biom_ct[-4], indiv_seeds_ct[-c(1,4)]) #left_joint requires unique names 

rownames(indiv_biom_seeds_ct) <- NULL 

colnames(indiv_biom_seeds_ct) <- c("Contrast",rep(c("ratio","p.value"),4))

indiv_biom_seeds_ct$Contrast <- gsub(" / ", " vs ", indiv_biom_seeds_ct$Contrast)


kbl(indiv_biom_seeds_ct, 
    longtable = FALSE, booktabs = TRUE, linesep = "", 
    caption = "Crop and rotation system effects on individual female aboveground mass and fecundity.") %>% 
    add_header_above(c(" " = 1, 
                       "Conventional herbicide \n corn weed management" = 2, 
                       "Low herbicide \n corn weed management" = 2,
                        "Conventional herbicide \n corn weed management" = 2, 
                       "Low herbicide \n corn weed management" = 2)) %>%
  add_header_above(c(" " = 1,
                    "Female individual aboveground mass" = 4, 
                    "Individual fecundity" = 4)) %>%
  column_spec(5, border_right = TRUE) %>%
   pack_rows("(A) - Crop phase effects", 1,7) %>%
    pack_rows("(B) - Crop species effects", 8,13) %>%
  landscape() %>%
  footnote(general = "C2: corn in the 2-year rotation, C3: corn in the 3-year rotation, C4: corn in the 4-year rotation, S2: soybean in the 2-year rotation, S3: soybean in the 3-year rotation; S4: soybean in the 4-year rotation, O3: oat in the 3-year rotation, O4: oat in the 4-year rotation, and A4: alfalfa in the 4-year rotation", threeparttable = TRUE, footnote_as_chunk = TRUE)
```

## Effects of weed management regimes and rotations on female aboveground mass and fecundity relationship {-}   
  
Since the treatment effects were statistically significant for both female aboveground mass and fecundity (Table \@ref(tab:ancova-jt)), we proceeded with finding the slopes and intercepts for each linear regression of fecundity against biomass. Different slopes were specified by including interaction terms between the covariate and treatment factors. A regression slope for each treatment was necessary. That the training and testing sets' data points were well mingled indicated that the established equations were robust (Figure \@ref(fig:full-p)). The equations in Table \@ref(tab:ci-full) could predict waterhemp fecundity parsimoniously from dried aboveground mass using the relevant context of crop and crop management. The presented means and SEs for the estimated intercepts and slopes were established from the whole data set.  
 

```{r ancova-jt, echo = FALSE}
### 18 means full compound symmetry model: Effects of crop identity and corn weed management on individual fecundity, mediated by individual biomass

## Keep complete cases only (389/391 entries)
fecundity18_sb <- fecundity18[complete.cases(fecundity18$Seed, fecundity18$Biomass), ]

allcrops.biom.seed.gls <- gls(log(Seed+1) ~ Block + 
                                log(Biomass + 0.005) + 
                                Crop_ID + Corn_weed_management +
                      Crop_ID:Corn_weed_management +
                      Crop_ID:log(Biomass + 0.005) +
                        Corn_weed_management:log(Biomass + 0.005) +
                      Crop_ID:Corn_weed_management:log(Biomass + 0.005),
  correlation=corCompSymm(form= ~1 | bt), #identifies each treatment within block
  data=fecundity18_sb)


allcrops.biom.seed.gls_jt <- joint_tests(emmeans(allcrops.biom.seed.gls ,
                                                 ~ Crop_ID * Corn_weed_management | Biomass,
                                                 at = list(Biomass = c(-0.5, 1.3)))) #to show the effects of biomass on fecundity

#diff intercept, diff slope for each CropID:Corn_weed_management combination, to remove intercept for ease of view
allcrops.biom.seed.gls_d <- gls(log(Seed+1) ~ -1 +
                      Crop_ID:Corn_weed_management +
                      Crop_ID:Corn_weed_management:log(Biomass + 0.005),
  correlation=corCompSymm(form= ~1 | bt), #identifies each treatment within block
  data=fecundity18_sb)

#summary(allcrops.aov2)
#for ease of view 

allcrops.biom.seed.gls_jt$`model term` <- gsub(":", " x ", allcrops.biom.seed.gls_jt$`model term`)
allcrops.biom.seed.gls_jt$`model term` <- gsub("_", " ", allcrops.biom.seed.gls_jt$`model term`)

allcrops.biom.seed.gls_jt_df <- print(allcrops.biom.seed.gls_jt, export = TRUE)


biom_seed_jt <- rbind(biomass.gls_df$summary,seeds.gls_df$summary, allcrops.biom.seed.gls_jt_df$summary)

rownames(biom_seed_jt) <- NULL

biom_seed_jt_df <- as.data.frame(biom_seed_jt)

biom_seed_jt_df[,2:4] <- sapply(biom_seed_jt_df[,2:4], as.numeric)

kbl(biom_seed_jt_df ,  booktabs = TRUE, linesep = "", 
    longtable = FALSE, digits = 2,
    col.names = c("Source of variation", "df1", "df2", "F.value", "p.value"),
    caption = "ANOVAs for effect of crop identity, corn weed management, and female aboveground mass on individual female aboveground mass (A), fecundity (B), and fecundity with aboveground mass covariate (C). Each combination of crop identity and corn weed management affected female aboveground mass and fecundity differently.") %>%
  pack_rows("(A) - Individual female aboveground mass. MSE = 2.02", 1,3) %>% 
  pack_rows("(B) - Individual fecundity. MSE = 3.43", 4,6) %>% 
  pack_rows("(C) - Individual fecundity with individual aboveground mass covariate. MSE = 1.01", 7,13) %>% 
  kable_styling(latex_options = c("scale_down")) %>%
  footnote(general = "C2: corn in the 2-year rotation, C3: corn in the 3-year rotation, C4: corn in the 4-year rotation, S2: soybean in the 2-year rotation, S3: soybean in the 3-year rotation; S4: soybean in the 4-year rotation, O3: oat in the 3-year rotation, O4: oat in the 4-year rotation, and A4: alfalfa in the 4-year rotation", threeparttable = T, footnote_as_chunk = TRUE)

# <https://tex.stackexchange.com/questions/594324/how-to-replace-all-with-or-x-in-an-anova-table>
```  
```{r, include=FALSE}
# Compare MSE of models for seed production estimation from biomass, seed gls and biomass gls  

 mean(residuals(allcrops.biom.seed.gls)^2)  #1.01

 mean(residuals(seeds.gls)^2)  #3.42714

 mean(residuals(biomass.gls)^2)  #2.02063
```

```{r ci-full, echo=FALSE, fig.height= 24, fig.width= 16}
#full data set from the previous chunk
allcrops_18 <- fecundity18_sb %>%
  mutate(Tercile = split_quantile(Biomass, 4)) %>% #
  group_by(Tercile, Crop_ID, Corn_weed_management) %>% 
  mutate(m_Biomass = mean(Biomass),
         log_Biomass = log(Biomass),
         log_Seed = log(Seed + 1))

models_ci <- allcrops_18 %>% 
  group_by(Crop_ID, Corn_weed_management) %>% 
           do(data.frame(tidy(lm(log(Seed+1) ~ log(Biomass + 0.005), 
                                 data = .), conf.int=TRUE )))

models_rsq <- allcrops_18 %>% 
  group_by(Crop_ID, Corn_weed_management) %>% 
           do(data.frame(tidy(summary(lm(log(Seed+1) ~ log(Biomass + 0.005), data = .), conf.int=TRUE )$r.squared)))
          
models_ci_df <- models_ci[,1:5] %>% 
  pivot_longer(cols=c(estimate, std.error)) %>% 
 pivot_wider(names_from = c(term, name), 
             values_from = value)

models_ci_rsq <- models_ci_df %>% left_join(models_rsq) 

kbl(models_ci_rsq , booktabs = TRUE, longtable = FALSE,
      col.names = c("Crop ID", "Corn \n weed management", "Estimate", "Std.error", "Estimate", "Std.error", " "),
          linesep = "",
          digits = 2, 
    caption = "Means and SEs for estimated linear regression of waterhemp fecundity (ln(seeds + 1)) versus biomass (ln(gram + 0.005)) indices intercepts and slopes, accompanied by the R$^2$ values of each equations.") %>%
  add_header_above(c("Effect" = 2 , "Intercept" = 2, "Slope" = 2, "R$^2$" = 1)) %>% 
  kable_styling(latex_options = c("scale_down")) %>%
  footnote(general = "C2: corn in the 2-year rotation, C3: corn in the 3-year rotation, C4: corn in the 4-year rotation, S2: soybean in the 2-year rotation, S3: soybean in the 3-year rotation; S4: soybean in the 4-year rotation, O3: oat in the 3-year rotation, O4: oat in the 4-year rotation, and A4: alfalfa in the 4-year rotation", threeparttable = T, footnote_as_chunk = TRUE)

```

```{r, include=FALSE}
# write model_ci_df in Dissertation folder to use for other manuscript (link to be updated). 
#write.csv(models_ci_df, "~/Documents/Dissertation/Demographic_AMATA/Fecundity/fecund_eq.csv", row.names = F)
```

```{r all means split, echo=FALSE, message=FALSE, warning=FALSE} 

allcrops_18_train <- allcrops_18 %>%
  sample_frac(0.8) #put 80% of the full data set into the training set

allcrops_18_test <- anti_join(allcrops_18, allcrops_18_train) #use the other 20% as a testing set

```


```{r all means test train, echo=FALSE}
# Train
fecund_train <- update(allcrops.biom.seed.gls, data = allcrops_18_train)

# Predict
allcrops_18_test$log_Seed_pred <- predict(fecund_train, allcrops_18_test) 

#error 
error.allcrops.biom.seed.gls = allcrops_18_test$log_Seed_pred - allcrops_18_test$log_Seed

```


```{r, full-p, echo=FALSE, warning = FALSE, fig.width = 8, fig.height = 10, fig.cap = "The black and red dots are values from training and testing sets, respectively. Each regression line was plotted for one crop identity by herbicide treatment using the training set. Biomass index = ln(gram biomass + 0.005) and Fecundity index = ln(seeds + 1)"}

# Change the vertical panel text  
# https://stackoverflow.com/questions/3472980/how-to-change-facet-labels


ggplot(data = allcrops_18_train, aes(x = log_Biomass, y = log_Seed)) +
   geom_smooth(method = "lm", se=TRUE, color="black", formula = y~x) +
   stat_poly_eq(formula = y~x, 
                aes(label = paste(..rr.label.., 
                                  sep = "~~~")),
                size = 6,
                parse = TRUE,
                label.y = 0.2,
                label.x = 0.9) +         
  facet_grid(Crop_ID ~  Corn_weed_management, 
             labeller = labeller(
        Corn_weed_management = c("conv" = "Corn weed management: conventional",
                                 "low" = "Corn weed management: low"))) +
    scale_y_continuous(limits = c(-3, 12),
                     expand = expansion(mult = c(0, 0.2))) +
  geom_point(size = 3) +
  geom_smooth(method = "lm") + 
    theme_bw()+
  theme(text=element_text(size=16),
        panel.margin.x=unit(1, "lines"))  +
    xlab("Biomass index") +   
    ylab("Fecundity index") +
  geom_point(data=allcrops_18_test, color = "red", size = 3)
```
