---
output:  
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
    number_sections: false
    extra_dependencies: ["float"]
---

```{r, include=FALSE}
library(emmeans)
library(here)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, 
                      message = FALSE,  dev=c("png")) 
                    #  fig.width = 16, 
                    #  fig.height = 16)#,
                      #full.fig.width = TRUE, out.width="100%")
library(tidyverse)
library(nlme)
library(kableExtra)
library(gridExtra)
library(magrittr)
library(mice)
source("functions.R")
RNGkind(sample.kind = "Rounding")
```

## Population aboveground mass and stand density {-}

In both years, population aboveground mass and stand density was strongly influenced by crop identity (Table \@ref(tab:pop-biom-dens-jt)). The rotation system in which a crop was grown also affected population aboveground mass and stand density, although not consistently between years (Table \@ref(tab:pbiom-dens-ct)).  

In 2018, population aboveground mass in the same crop species was comparable across rotations except for corn grown in the 2-year (C2) versus 4-year rotation (C4) (p-value = 0.043). In 2019, population aboveground mass in the same crop was significantly different across rotations, except for corn in the 2-year (C2) versus 3-year rotation (C3) (p-value = 0.968) and soybean in the 3-year (S3) versus 4-year rotation (S4) (p-value = 1). Averaged across rotations, population aboveground mass was comparable in 2018 for corn versus alfalfa (p-value = 0.2509) and soybean versus oat (p-value = 0.504), but 10- to 2580-fold different in the other ten pairs (p-values < 0.01).   

In 2018, population stand density in the same crop species was comparable across the rotations. In 2019, population stand density in the same crop species was comparable for soybean (p-values = 0.1256 and 1) and C2 versus C3 (p-value = 0.9284), but significantly different for the other corn comparisons and for oat in the 3-year (O3) versus 4-year rotation (O4). Averaged over rotations, population stand density was comparable in 2018 between soybean and alfalfa (p-value = 0.766), but 5- to 1330-fold different in the other eight pairs of comparison (p-values < 0.001).   

In 2018, population aboveground mass was the highest in soybean and oat (Figure \@ref(fig:pop-biom-dens-all)A) because soybean weed management was ineffective and herbicide was intentionally not applied in oat. The legacy of an ineffective weed management program in 2018 soybean plots was observed in 2019 oat plots where population aboveground mass and stand density were the highest among all the crop identities ((Figure \@ref(fig:pop-biom-dens-all)B). High stand density in 2019 oat plots was also due to uneven oat establishment. The change in 2019 in weed management for soybean substantially reduced the waterhemp pressure on soybean (Figure \@ref(fig:pop-biom-dens-all)B and \@ref(fig:pop-biom-dens-all)D).
  

```{r, include=FALSE}
amata18 <- read_csv("../2-Data/Clean/AMATA_18_clean.csv",
                    col_types = cols(Plot = col_factor(), 
                                     Block = col_factor(), 
                                     Crop = col_factor(),
                                     Crop_ID = col_factor(),
                                     Corn_weed_management = col_factor(),
                                     Year = col_character(),
                                     Male = col_integer(), 
                                     Female = col_integer()))



amata18$Crop_ID <- factor(amata18$Crop_ID, levels = c("C2", "S2",
                                                                "C3", "S3", "O3",
                                                                "C4", "S4", "O4", "A4"))

## Make sure that Block, Crop_ID, and Corn_weed_management are factors
amata18 <- amata18 %<>%
  mutate_at(c("Block","Crop_ID","Corn_weed_management"),funs(factor(.)))




amata19 <- read_csv("../2-Data/Clean/AMATA_19_clean.csv",
                    col_types = cols(Plot = col_factor(), 
                                     Block = col_factor(), 
                                     Crop = col_factor(),
                                     Crop_ID = col_factor(),
                                     Corn_weed_management = col_factor(),
                                     Year = col_character(),
                                     Male = col_integer(), 
                                     Female = col_integer()))

amata19$Crop_ID <- factor(amata19$Crop_ID, levels = c("C2", "S2",
                                                                "C3", "S3", "O3",
                                                                "C4", "S4", "O4", "A4"))

amata19 <- amata19 %<>%
  mutate_at(c("Block","Crop_ID", "Corn_weed_management", "Year"),funs(factor(.)))

```


```{r, include=FALSE}
## How did crop identity and corn weed management affect AMATA aboveground mass in 2018? ##
#Find the smallest non-zero value in aboveground mass: 

#min(amata18$g_m_sq[amata18$g_m_sq > 0])
#min(amata19$g_m_sq[amata19$g_m_sq > 0])

pop_biom18 <- lm(log(g_m_sq + 0.00025) ~ Block +  Crop_ID*Corn_weed_management, 
                   data = amata18)

biom_jt_18 <- joint_tests(emmeans(pop_biom18, c("Crop_ID", "Corn_weed_management")))

# Aesthetic: replace : with x for interaction, and remove "_" in Corn_weed_management
biom_jt_18$`model term` <- gsub(":", " x ", biom_jt_18$`model term`)
biom_jt_18$`model term` <- gsub("_", " ", biom_jt_18$`model term`)

biom_jt_18_df <- print(biom_jt_18, export = TRUE)

## How did crop identity and corn weed management affect AMATA aboveground mass in 2018? ##

pop_biom19 <- lm(log(g_m_sq + 0.002) ~ Block +  Crop_ID*Corn_weed_management,
                 data = amata19)

biom_jt_19 <- joint_tests(emmeans(pop_biom19, c("Crop_ID", "Corn_weed_management")))

# Aesthetic: replace : with x for interaction, and remove "_" in Corn_weed_management
biom_jt_19$`model term` <- gsub(":", " x ", biom_jt_19$`model term`)
biom_jt_19$`model term` <- gsub("_", " ", biom_jt_19$`model term`)


biom_jt_19_df <- print(biom_jt_19, export = TRUE)

#resid_panel(pop_biom19) 

```


```{r , include=FALSE}
## How did crop identity and corn weed management affect AMATA density in 2018? ##
#Find the smallest non-zero value in plant density:
#min(amata18$plant_m_sq[amata18$plant_m_sq > 0])
#min(amata19$plant_m_sq[amata19$plant_m_sq > 0])

pop_dens18 <- lm(log(plant_m_sq + 0.025) ~ Block + Crop_ID*Corn_weed_management,
                 data = amata18)


dens_jt_18 <- joint_tests(emmeans(pop_dens18, c("Crop_ID", "Corn_weed_management")))

# Aesthetic: replace : with x for interaction, and remove "_" in Corn_weed_management

dens_jt_18$`model term` <- gsub(":", " x ", dens_jt_18$`model term`)
dens_jt_18$`model term` <- gsub("_", " ", dens_jt_18$`model term`)

dens_jt_18_df <- print(dens_jt_18, export = TRUE)

## How did crop identity and corn weed management affect AMATA density in 2019? ##


pop_dens19 <- lm(log(plant_m_sq + 0.025) ~ Block + Crop_ID*Corn_weed_management,
                 data = amata19)


dens_jt_19 <- joint_tests(emmeans(pop_dens19, c("Crop_ID", "Corn_weed_management")))

# Aesthetic: replace : with x for interaction, and remove "_" in Corn_weed_management
dens_jt_19$`model term` <- gsub(":", " x ", dens_jt_19$`model term`)
dens_jt_19$`model term` <- gsub("_", " ", dens_jt_19$`model term`)

dens_jt_19_df <- print(dens_jt_19, export = TRUE)
```


```{r, include=FALSE}
# Merge 2018 population biomass (left) and density (right) ANOVA tables side by side
biom_dens_18 <- cbind(biom_jt_18_df$summary, dens_jt_18_df$summary[,c(4,5)])

biom_dens_18_df <- as.data.frame(biom_dens_18)

# convert df1, df2, and F.value to numeric to round in the kbl() step
biom_dens_18_df[,c(2:4,6)] <- sapply(biom_dens_18_df[,c(2:4,6)], as.numeric)

# Merge 2019 population biomass (left) and density (right) ANOVA tables side by side
biom_dens_19 <- cbind(biom_jt_19_df$summary, dens_jt_19_df$summary[,c(4,5)])

biom_dens_19_df <- as.data.frame(biom_dens_19)

# convert df1, df2, and F.value to numeric to round in the kbl() step
biom_dens_19_df[,c(2:4,6)] <- sapply(biom_dens_19_df[,c(2:4,6)], as.numeric)

biom_dens <-  cbind(biom_dens_18_df, biom_dens_19_df) #left_joint will need unique column names
rownames(biom_dens) <- NULL
```

```{r pop-biom-dens-jt, echo=FALSE}
biom_dens[,-c(8:10)] %>%
kbl(longtable = FALSE, booktabs = TRUE, digits = 2,
    col.names = c("Source of variation", "df1", "df2", rep(c("F.value", "p.value"), 4)),
    caption = "ANOVAs of crop identity and corn weed management effects on waterhemp population aboveground mass and stand density. Crop identity was the only influential factor on both population aboveground mass and stand density in 2018 and 2019.") %>% 
add_header_above(c(" " = 3, 
                     "Population \n aboveground mass" = 2, 
                     "Population \n stand density" = 2,
                     "Population \n aboveground mass" = 2, 
                     "Population \n stand density" = 2)) %>%
  add_header_above(c(" " = 3, "2018" = 4, "2019" = 4)) %>% 
  column_spec(7, border_left = FALSE, border_right = TRUE) %>%
  landscape() 
```
 
```{r, include=FALSE}
## Calculate marginal means by Crop_ID, because Corn_weed_management effect was not significant ## 
biom_emm_18 <- emmeans(pop_biom18, "Crop_ID", type="response") 
biom_emm_19 <- emmeans(pop_biom19, "Crop_ID", type = "response") 

dens_emm_18 <- emmeans(pop_dens18, "Crop_ID", type = "response")
dens_emm_19 <- emmeans(pop_dens19, "Crop_ID", type = "response")
```


```{r, include=FALSE}
## population aboveground mass 2018
bp18 <- arrow_all(biom_emm_18) + 
  xlab(expression(g/m^2)) +
    ylab("Crop ID") + 
    ggtitle("(A) 2018 population aboveground mass") 

## population aboveground mass 2019
bp19 <- arrow_all(biom_emm_19) + 
  xlab(expression(g/m^2)) +
    ylab("Crop ID") + 
    ggtitle("(B) 2019 population aboveground mass")  + xlim(-1,170)


## population density 2018
dp18 <- arrow_all(dens_emm_18) +
  xlab(expression(plant/m^2)) +
    ylab("Crop ID") + 
    ggtitle("(C) 2018 population stand density")   + xlim(-1,170)

## population density 2019
dp19 <- arrow_all(dens_emm_19) + 
  xlab(expression(plant/m^2)) +
    ylab("Crop ID") + 
  ggtitle("(D) 2019 population stand density")  
```


```{r pop-biom-dens-all, fig.cap = "Waterhemp population aboveground mass and stand density averaged over corn weed managements. The abbreviations on the x-axis are crop identities, which are the combinations of the first letter in crop species names and the rotation to which the crops belonged (C2: corn in the 2-year rotation, C3: corn in the 3-year rotation, C4: corn in the 4-year rotation, S2: soybean in the 2-year rotation, S3: soybean in the 3-year rotation; S4: soybean in the 4-year rotation, O3: oat in the 3-year rotation, O4: oat in the 4-year rotation, and A4: alfalfa in the 4-year rotation). The black dots are estimated marginal means. The blue bars are 95% confidence intervals. The red arrows reflect the comparison among means. Overlapping arrows indicate non-significant differences.",  echo = FALSE, fig.width=8, fig.height=8} 

# If use the patchwork package to arrange: bp <-  (bp18 + bp19) / (dp18 + dp19)
gridExtra::grid.arrange(bp18, bp19, dp18, dp19, nrow = 2) 
```  



```{r, include=FALSE}
#### 2018 population aboveground mass ####

#  Crop rotation effects: Calculate marginal means by crop species within each rotation followed by contrast (corn weed management effect was NS)

pop_biom_corn_18 <- emmeans(pop_biom18, ~ Crop_ID , 
                            infer = c(FALSE,TRUE),  
                            type = "response",
                            at = list(Crop_ID = c( "C2", "C3", "C4")))

pop_biom_corn_ct18 <- contrast(pop_biom_corn_18,
                               "pairwise", 
                               type = "response",
                               infer = c(FALSE,TRUE)) %>% 
  print(export = TRUE)

pop_biom_soy_18 <- emmeans(pop_biom18, ~ Crop_ID , 
                           infer = c(FALSE,TRUE), 
                           type = "response",
                           at = list(Crop_ID = c( "S2", "S3", "S4")))

pop_biom_soy_ct18 <- contrast(pop_biom_soy_18,
                              "pairwise",
                              type = "response",
                              infer = c(FALSE,TRUE)) %>%
  print(export = TRUE) #since S3 not significantly diff from S4, can do S2 vs (s3+S4)/2

pop_biom_oat_18 <- emmeans(pop_biom18, ~ Crop_ID ,
                           infer = c(FALSE,TRUE), 
                           type = "response", 
                           at = list(Crop_ID = c( "O3", "O4")))

pop_biom_oat_ct18 <- contrast(pop_biom_oat_18, 
                              "pairwise",
                              type = "response",
                              infer = c(FALSE,TRUE)) %>% 
  print(export = TRUE)

## Crop species effects: Calculate marginal means by crop species averaged over rotation followed by contrast (corn weed management effect was NS) 

# Add crop species name as a grouping factor 
biom_18_grid <- ref_grid(pop_biom18)

Crop <- factor(c("corn", "soybean",
                 "corn", "soybean", "oat", 
                 "corn", "soybean", "oat", "alfalfa"),
                     levels = c("oat", "soybean", "corn", "alfalfa"))


biom_emm_18_grid_crop <- add_grouping(biom_18_grid , "Crop", "Crop_ID", Crop)

# crop contrast, averaged over rotations
pop_biom_crop18 <- emmeans(biom_emm_18_grid_crop, ~ Crop, infer = c(FALSE,TRUE),  type = "response") 

pop_biom_crop_ct18 <- contrast(pop_biom_crop18, "pairwise", type = "response", infer = c(FALSE,TRUE)) %>% print(export = TRUE)

## Compile a table of contrast for 2018 population biomass 
pop_biom_ct18 <- rbind(pop_biom_corn_ct18$summary,
                        pop_biom_soy_ct18$summary,
                        pop_biom_oat_ct18$summary,
                     pop_biom_crop_ct18$summary)


pop_biom_ct18_df <- as.data.frame(pop_biom_ct18)

#convert all columns except "p.values" to numeric to round
pop_biom_ct18_df[,2:6] <- sapply(pop_biom_ct18_df[,2:6],as.numeric)

pop_biom_ct18_rounded <- pop_biom_ct18_df %>%
  mutate(across(where(is.numeric), ~ as.numeric(sprintf('%.2f', .)))) 
```



```{r, include=FALSE}
#### 2019 population aboveground mass ####

#  Rotation effects: Calculate marginal means by the same crop species in different rotation followed by contrast (corn weed management effect was NS)
pop_biom_corn_19 <- emmeans(pop_biom19, ~ Crop_ID , 
                            infer = c(FALSE,TRUE),
                            type = "response",
                            at = list(Crop_ID = c( "C2", "C3", "C4")))

pop_biom_corn_ct19 <- contrast(pop_biom_corn_19,
                               "pairwise", 
                               type = "response", 
                               infer = c(FALSE,TRUE)) %>%
  print(export = TRUE)

pop_biom_soy_19 <- emmeans(pop_biom19, ~ Crop_ID ,
                           infer = c(FALSE,TRUE), 
                           type = "response",
                           at = list(Crop_ID = c( "S2", "S3", "S4")))

pop_biom_soy_ct19 <- contrast(pop_biom_soy_19, 
                              "pairwise",
                              type = "response",
                              infer = c(FALSE,TRUE)) %>%
  print(export = TRUE) #since S3 not significantly diff from S4, can do S2 vs (S3+S4)/2

pop_biom_oat_19 <- emmeans(pop_biom19, ~ Crop_ID ,
                           infer = c(FALSE,TRUE), 
                           type = "response", 
                           at = list(Crop_ID = c( "O3", "O4")))

pop_biom_oat_ct19 <- contrast(pop_biom_oat_19, 
                              "pairwise", 
                              type = "response", 
                              infer = c(FALSE,TRUE)) %>%
  print(export = TRUE)

## Crop species effects: Calculate marginal means by crop species averaged over rotation followed by contrast (corn weed management effect was NS) 

# Add crop species name as a grouping factor 
biom_19_grid <- ref_grid(pop_biom19)

biom_emm_19_grid_crop <- add_grouping(biom_19_grid , "Crop", "Crop_ID", Crop)

# crop contrast, averaged over rotations
pop_biom_crop19 <- emmeans(biom_emm_19_grid_crop, ~ Crop,
                           infer = c(FALSE,TRUE),  type = "response") 

pop_biom_crop_ct19 <- contrast(pop_biom_crop19, 
                               "pairwise", 
                               type = "response",
                               infer = c(FALSE,TRUE)) %>% 
  print(export = TRUE)


## Compile a table of contrast for 2019 population biomass 
pop_biom_ct19 <- rbind( pop_biom_corn_ct19$summary,
                        pop_biom_soy_ct19$summary,
                        pop_biom_oat_ct19$summary,
                     pop_biom_crop_ct19$summary)

pop_biom_ct19_df <- as.data.frame(pop_biom_ct19)

#convert all columns except "p.values" to numeric to round
pop_biom_ct19_df[,2:6] <- sapply(pop_biom_ct19_df[,2:6],as.numeric)

pop_biom_ct19_rounded <- pop_biom_ct19_df %>%
  mutate(across(where(is.numeric), ~ as.numeric(sprintf('%.2f', .))))
```

```{r pbiom-ct, echo=FALSE}
## Compile a table of aboveground mass over 2 years
pop_biom_ct <- cbind(pop_biom_ct18_rounded, pop_biom_ct19_rounded)

rownames(pop_biom_ct) <- NULL 
pop_biom_ct_df <-  pop_biom_ct[,-c(5,8,12)] #remove the duplicated row names and 2 null value cols

```


```{r, echo=FALSE}
#### 2018 population density ####

## Crop species effects: Calculate marginal means by crop species averaged over rotation followed by contrast (corn weed management effect was NS) 

pop_dens_corn18 <-  emmeans(pop_dens18, ~ Crop_ID ,
                            infer = c(FALSE,TRUE), 
                            type = "response", 
                            at = list(Crop_ID = c( "C2", "C3", "C4")))

pop_dens_corn_ct18 <- contrast(pop_dens_corn18 ,
                               "pairwise", 
                               type = "response",
                               infer = c(FALSE,TRUE)) %>% 
  print(export = TRUE)

pop_dens_soy18 <- emmeans(pop_dens18, ~ Crop_ID,
                          infer = c(FALSE,TRUE),
                          type = "response", 
                          at = list(Crop_ID = c("S2", "S3", "S4"))) 

pop_dens_soy_ct18 <- contrast(pop_dens_soy18, 
                              "pairwise",
                              type = "response", 
                              infer = c(FALSE,TRUE)) %>%
  print(export = TRUE)

pop_dens_oat18 <- emmeans(pop_dens18, ~ Crop_ID,
                          infer = c(FALSE,TRUE),
                          type = "response", 
                          at = list(Crop_ID = c("O3", "O4")))

pop_dens_oat_ct18 <- contrast(pop_dens_oat18, 
                              "pairwise", 
                              type = "response", 
                              infer = c(FALSE,TRUE))  %>%
  print(export = TRUE)


#  Crop phase effects: Calculate marginal means by crop species within each rotation followed by contrast (corn weed management effect was NS) -- 2018 population density

# Add crop species name as a grouping factor 
dens_18_grid <- ref_grid(pop_dens18)

# add crop species as a grouping factor
dens_emm_18_grid_crop <- add_grouping(dens_18_grid , "Crop", "Crop_ID", Crop)

pop_dens_crop18 <- emmeans(dens_emm_18_grid_crop, ~ Crop, 
                           infer = c(FALSE,TRUE),  
                           type = "response") 

pop_dens_crop_ct18 <- contrast(pop_dens_crop18, 
                               "pairwise", 
                               type = "response", 
                               infer = c(FALSE,TRUE)) %>% 
  print(export = TRUE)

# Compile a contrast table for 2018 population density
pop_dens_ct18 <- rbind(pop_dens_corn_ct18$summary,
                       pop_dens_soy_ct18$summary,
                       pop_dens_oat_ct18$summary,
                       pop_dens_crop_ct18$summary)


pop_dens_ct18_df <- as.data.frame(pop_dens_ct18)

#convert all columns except "p.values" to numeric to round
pop_dens_ct18_df[,2:6] <- sapply(pop_dens_ct18_df[,2:6], as.numeric)

pop_dens_ct18_rounded <- pop_dens_ct18_df %>%
  mutate(across(where(is.numeric), ~ as.numeric(sprintf('%.2f', .))))  
```


```{r, echo=FALSE}
#### 2019 population density ####

##  Crop rotation effects: Calculate marginal means by crop species within each rotation followed by contrast (corn weed management effect was NS) 

pop_dens_corn19 <-  emmeans(pop_dens19, ~ Crop_ID ,
                            infer = c(FALSE,TRUE), 
                            type = "response", 
                            at = list(Crop_ID = c( "C2", "C3", "C4")))

pop_dens_corn_ct19 <- contrast(pop_dens_corn19, 
                               "pairwise",
                               type = "response", 
                               infer = c(FALSE,TRUE)) %>%
  print(export = TRUE)

pop_dens_soy19 <- emmeans(pop_dens19, ~ Crop_ID,
                          infer = c(FALSE,TRUE),
                          type = "response", 
                          at = list(Crop_ID = c("S2", "S3", "S4"))) 

pop_dens_soy_ct19 <- contrast(pop_dens_soy19, 
                              "pairwise", 
                              type = "response",
                              infer = c(FALSE,TRUE)) %>%
  print(export = TRUE)

pop_dens_oat19 <- emmeans(pop_dens19, ~ Crop_ID,
                          infer = c(FALSE,TRUE),
                          type = "response", 
                          at = list(Crop_ID = c("O3", "O4")))

pop_dens_oat_ct19 <- contrast(pop_dens_oat19,
                              "pairwise", 
                              type = "response", 
                              infer = c(FALSE,TRUE)) %>% 
  print(export = TRUE)


## Crop species effects: Calculate marginal means by crop species averaged over rotation followed by contrast (corn weed management effect was NS) 

# add crop species as a grouping factor
dens_19_grid <- ref_grid(pop_dens19)
dens_emm_19_grid_crop <- add_grouping(dens_19_grid , "Crop", "Crop_ID", Crop)

# crop contrasts, averaged over rotations
pop_dens_crop19 <- emmeans(dens_emm_19_grid_crop, ~ Crop,
                           infer = c(FALSE,TRUE),
                           type = "response")

pop_dens_crop_ct19 <- contrast(pop_dens_crop19,
                               "pairwise", 
                               type = "response",
                               infer = c(FALSE,TRUE)) %>%
  print(export = TRUE)


# Compile a contrast table for 2019 population density
pop_dens_ct19 <- rbind(pop_dens_corn_ct19$summary,
                       pop_dens_soy_ct19$summary,
                       pop_dens_oat_ct19$summary,
                       pop_dens_crop_ct19$summary)


pop_dens_ct19_df <- as.data.frame(pop_dens_ct19)

#convert all columns except "p.values" to numeric to round
pop_dens_ct19_df[,2:6] <- sapply(pop_dens_ct19_df[,2:6],as.numeric)

pop_dens_ct19_rounded <- pop_dens_ct19_df %>%
  mutate(across(where(is.numeric), ~ as.numeric(sprintf('%.2f', .))))

```


```{r pbiom-dens-ct, echo=FALSE} 
## Merge 2018 population biomass and density contrast tables
pop_biom_dens_18 <- pop_biom_ct18_rounded[,-c(3:6)] %>% 
  left_join(pop_dens_ct18_rounded[,-c(3:6)], by = "contrast")

## Merge 2019 population biomass and density contrasts
pop_biom_dens_19 <- pop_biom_ct19_rounded[,-c(3:6)] %>% 
  left_join(pop_dens_ct19_rounded[,-c(3:6)], by = "contrast")


## Merge density and biomass contrasts
pop_biom_dens_ct <- pop_biom_dens_18 %>% 
  left_join( pop_biom_dens_19 , by = "contrast")

rownames(pop_biom_dens_ct) <- NULL  

pop_biom_dens_ct$contrast <- gsub(" / ", " vs ", pop_biom_dens_ct$contrast)


pop_biom_dens_ct%>%
kbl(booktabs = TRUE, linesep = "", longtable = FALSE, digits = 2,
    col.names = c("Contrast", rep(c("ratio", "p.value"),4)),
    caption = "Rotation system and crop effects on population aboveground mass and stand density.") %>% 
  add_header_above(c(" " = 1, 
                     "Population \n aboveground mass" = 2, 
                     "Population \n stand density" = 2,
                     "Population \n aboveground mass" = 2, 
                     "Population \n stand density" = 2)) %>%
  add_header_above(c(" " = 1, "2018" = 4, "2019" = 4)) %>% 
  pack_rows("(A) - Rotation system effects", 1,7) %>% 
  pack_rows("(B) - Crop species effects", 8,13) %>% 
    column_spec(5,border_left = FALSE, border_right = TRUE) %>%
    footnote(general = "Some zero values are due to rounding. C2: corn in the 2-year rotation, C3: corn in the 3-year rotation, C4: corn in the 4-year rotation, S2: soybean in the 2-year rotation, S3: soybean in the 3-year rotation; S4: soybean in the 4-year rotation, O3: oat in the 3-year rotation, O4: oat in the 4-year rotation, and A4: alfalfa in the 4-year rotation", threeparttable = TRUE, footnote_as_chunk = TRUE)
```


## Population sex ratio {-}

Population stand density was included to improve the precision of estimates of population sex ratios (Table \@ref(tab:sexr18-covar-jt)C versus \@ref(tab:sexr18-covar-jt)A). The population sex ratio in 2018 differed significantly among treatments, at different population stand densities within each treatment (p-value = 0.0155, Table \@ref(tab:sexr18-covar-jt) and Figure \@ref(fig:sexr18-dens-arrow)). Therefore, sex ratios in the same treatment were evaluated at four population densities, i.e., 1, 5, 50, and 500 plants/m$^2$, to illustrate that three-way interaction (Figure \@ref(fig:sexr18-dens-arrow)). Female-biasedness was more likely if a waterhemp population was grown in oat and alfalfa. None of the waterhemp populations grown in corn and soybean expressed gender biasedness. It is unclear whether the corn weed management program had a significant effect on gender biasedness given the magnitude of the variance (Figure \@ref(fig:sexr18-dens-arrow)).  


We defined a useful imputed data set to be a set that resulted in fully estimable marginal means for sex ratio comparison across all treatments, which was achievable with non-zeros in female and male categories in at least one replication among the four blocks for the missing observations in the 2019 original sex data. Unlike the 2018 data, the sex ratio in 2019 was analyzed without the covariates because none of the covariates improved the goodness of fit for the analysis model. With m = 24, five imputed data sets were useful (Appendix B). The significance and influence of treatment factors and their interaction in the imputed data sets for waterhemp sex ratio in 2019 were consistent with those of the 2018 data (Figure \@ref(fig:sexr19-arrow)). In 21 out of 24 sets, sex ratio in 2019 was affected by crop identity (Figure \@ref(fig:sexr19-arrow)B and \@ref(fig:sexr19-arrow)C). Female biasedness was observed in oat and alfalfa but not in corn and soybean (Figure \@ref(fig:sexr19-arrow)A).     

```{r, include=FALSE, warning=FALSE, message=FALSE}
## Did Crop_ID and Corn weed management had any effect on 2018 population sex ratio?
sexed18.glm <- glm(cbind(Female, Male) ~ Block +  Crop_ID*Corn_weed_management,
  data=amata18, family=quasibinomial(link = "logit"))
```


```{r type3-18, echo=FALSE}
#https://stackoverflow.com/questions/69784123/obtain-f-ratio-and-p-value-for-the-continuous-predictor?noredirect=1#comment123365815_69784123 

sexed18.emm <- emmeans(sexed18.glm, c("Crop_ID", "Corn_weed_management"), type = "response")

sexed18_jt <- joint_tests(sexed18.emm )
sexed18_jt$`model term` <- gsub(":", " x ", sexed18_jt$`model term`)
sexed18_jt$`model term` <- gsub("_", " ", sexed18_jt$`model term`)

sexed18_jt_df <- print(sexed18_jt, export = TRUE)
  
row.names(sexed18_jt_df) <- NULL

#<https://pdixon.stat.iastate.edu/stat511/Rcode/trout.r>
```


```{r, include=FALSE}
# Examine marginal means by Crop_ID 
plot(sexed18.emm, by = "Corn_weed_management", comparisons = TRUE) +
  coord_flip() + theme_bw()

```


```{r, include=FALSE}
## Did population aboveground mass, Crop_ID and Corn weed management had any effect on 2018 population sex ratio?

sexr18_biom_glm3 <- glm(cbind(Female, Male) ~ Block + 
                          Crop_ID + Corn_weed_management + 
                          log(g_m_sq + 0.00025) +
                        Crop_ID:Corn_weed_management + 
                        log(g_m_sq + 0.00025):Crop_ID +
                        log(g_m_sq + 0.00025):Corn_weed_management +
                        log(g_m_sq + 0.00025):Crop_ID:Corn_weed_management ,
  data=amata18, family=quasibinomial(link = "logit"))

## Did population density, Crop_ID and Corn weed management had any effect on 2018 population sex ratio?

sexr18_dens_glm3 <- glm(cbind(Female, Male) ~ Block  + 
                          Crop_ID + Corn_weed_management +
                          log(plant_m_sq + 0.025)  +
                        Crop_ID:Corn_weed_management + 
                        log(plant_m_sq + 0.025):Crop_ID +
                        log(plant_m_sq + 0.025):Corn_weed_management +
                        log(plant_m_sq + 0.025):Crop_ID:Corn_weed_management ,
  data=amata18, family=quasibinomial(link = "logit"))

#<http://web.pdx.edu/~newsomj/cdaclass/ho_glm.pdf>
```



```{r sexr18-covar-jt, echo=FALSE}

## Marginal means averaged by Blocks for population biomass, crop ID, and corn weed management effects on population ratio 
sexr18_biom_emm <- emmeans(sexr18_biom_glm3, 
                           ~ Crop_ID * Corn_weed_management | g_m_sq,
                           at = list(g_m_sq = c(-1.5, 3)))

## ANOVA table
sexr18_biom_jt <- joint_tests(sexr18_biom_emm) 
  

## Marginal means averaged by Blocks for population density, crop ID, and corn weed management effects on population ratio 
sexr18_dens_emm <- emmeans(sexr18_dens_glm3, 
                           ~ Crop_ID * Corn_weed_management | plant_m_sq,
                           at = list(plant_m_sq = c(-0.5, 1.3)))
## ANOVA table
sexr18_dens_jt <- joint_tests(sexr18_dens_emm) 

### Merge 2 ANOVA tables 
sexr18_covar_jt <- rbind(sexed18_jt, sexr18_biom_jt, sexr18_dens_jt)

sexr18_covar_jt$`model term` <- gsub(":", " x ", sexr18_covar_jt$`model term`) 
sexr18_covar_jt$`model term` <- gsub("g_m_sq", "Population aboveground mass", sexr18_covar_jt$`model term`) 

sexr18_covar_jt$`model term` <- gsub("plant_m_sq", "Population stand density", sexr18_covar_jt$`model term`) 

sexr18_covar_jt$`model term` <- gsub("_", " ", sexr18_covar_jt$`model term`) 

rownames(sexr18_covar_jt) <- NULL


sexr18_covar_df <- print(sexr18_covar_jt, export = TRUE)

sexr18_covar_df <- as.data.frame(sexr18_covar_df$summary)

sexr18_covar_df$F.ratio <- as.numeric(sexr18_covar_df$F.ratio)

sexr18_covar_rounded <- sexr18_covar_df %>%
  mutate(across(where(is.numeric), ~ as.numeric(sprintf('%.2f', .)))) %>%
#  mutate(across(where(is.numeric), as.character)) %>% #remove trailing zeros
  as_tibble # prevent adding trailing zeros later

kbl(sexr18_covar_rounded, longtable = FALSE, booktabs = TRUE, linesep = "",
    col.names = c("Source of variation", "df1", "df2", "F.value", "p.value"), 
     caption = "ANOVAs of crop identity, herbicide, and covariate effects on population sex ratio using 2018 data. With population aboveground mass covariate included (B), crop identity was the only influential factor on population sex ratio. With population stand density covariate included (C), sex ratio responded differently in each treatment and stand density combination.") %>%
  pack_rows("(A) no covariate. Residual deviance = 165.9, dispersion = 3.32.", 1,3) %>% 
  pack_rows("(B) with population aboveground mass covariate. Residual deviance = 104.3, dispersion = 3.24.", 4,10) %>% 
  pack_rows("(C) with population stand density covariate. Residual deviance = 82.12, dispersion = 2.54.", 11,17) %>% 
  kable_styling(latex_options = c("scale_down")) %>%
  landscape() 
```
 


```{r, include=FALSE}
## Customize lable for aesthetics
#https://stackoverflow.com/questions/70406886/edit-emmeans-arrow-plots-facet-text
custom_labels <- as_labeller(function(x){
     return(paste0("Corn weed management: ", c("conventional", "low")))
})

## Population sex ratio at 1 plant/m2 density
sexr18_dens_emm_1 <- emmeans(sexr18_dens_glm3, 
                             c("Crop_ID" , "Corn_weed_management" ),
                             type = "response", infer = c(TRUE,TRUE),
                             at=list(plant_m_sq=1))

dens_1 <- arrow_split(sexr18_dens_emm_1) + ggtitle(expression((A)~1~plants/m^2)) 


## Population sex ratio at 5 plant/m2 density
sexr18_dens_emm_5 <- emmeans(sexr18_dens_glm3, 
                             c("Crop_ID" , "Corn_weed_management" ), 
                             type = "response", infer = c(TRUE,TRUE),
                             at=list(plant_m_sq=5))

dens_5 <- arrow_split(sexr18_dens_emm_5) + ggtitle(expression((C)~5~plants/m^2)) 


## Population sex ratio at 50 plant/m2 density
sexr18_dens_emm_50 <- emmeans(sexr18_dens_glm3,
                              c("Crop_ID" , "Corn_weed_management" ),
                              type = "response", infer = c(TRUE,TRUE), 
                              at=list(plant_m_sq=50))

dens_50 <- arrow_split(sexr18_dens_emm_50) + ggtitle(expression((C)~50~plants/m^2)) 


## Population sex ratio at 500 plant/m2 density
sexr18_dens_emm_500 <- emmeans(sexr18_dens_glm3,
                               c("Crop_ID" , "Corn_weed_management" ), 
                               type = "response", infer = c(TRUE,TRUE),
                               at=list(plant_m_sq=500))

dens_500 <- arrow_split(sexr18_dens_emm_500) + ggtitle(expression((C)~500~plants/m^2)) 
```

```{r sexr18-dens-arrow, fig.cap="Waterhemp population sex ratios under 54 combinations of experimental treatments and population stand densities. The abbreviations on the x-axis are crop identities, which are the combinations of the first letter in crop species names and the rotation to which the crops belonged (C2: corn in the 2-year rotation, C3: corn in the 3-year rotation, C4: corn in the 4-year rotation, S2: soybean in the 2-year rotation, S3: soybean in the 3-year rotation; S4: soybean in the 4-year rotation, O3: oat in the 3-year rotation, O4: oat in the 4-year rotation, and A4: alfalfa in the 4-year rotation). The dashed lines mark sex ratio parity. The black dots are estimated marginal means. The blue bars are 95% confidence intervals. The red arrows reflect the comparisons among means. Overlapping arrows indicate non-significant differences.", echo = FALSE, fig.width=8, fig.height=10} 
gridExtra::grid.arrange(dens_1, dens_5, dens_50, dens_500, nrow = 2) 
```



```{r, echo=FALSE}
## 2019 sex ratio as is (before imputation)

sexed19_mis <- read_csv(here("2-Data/Clean/sexed19_mis.csv"), 
    col_types = cols(Plot = col_factor(), 
        Quadrat = col_factor(), 
        Cohort = col_factor(), 
        Block = col_factor(), 
        Crop = col_factor(),
        Crop_ID = col_factor(),
        Rotation = col_factor(),
         Herbicide = col_factor(),
        Corn_weed_management = col_factor(),
        Number_begin = col_integer(), 
        Total = col_integer(), 
        Female = col_integer(),
        Male = col_integer(), 
        Unknown = col_integer(), 
        Total_sexed = col_integer(), 
        Year = col_character()))

#summary(sexed19_mis)
```

```{r, echo=FALSE} 
## Categorical, independent variables are included, except quadrats. 

sexed19_resp1 <- sexed19_mis %>% 
  dplyr::select(Block, Crop_ID, Corn_weed_management, Female, Male, Total, Number_begin)

#trial 1, see if lambda and fmi are small, m = 24 = 4 cores x 6 imputations/core

#categorical variables with no missing cells are included 

sexed19_imp1_wide <- parlmice(sexed19_resp1 , 
                              cluster.seed = 500,
                              print = FALSE,
                              n.core = 4,
                              n.imp.core = 6) #cluster.seed = 500, identical to Appendix B's parlmice calls


sexed19_imp1_long <- sexed19_imp1_wide %>%
  mice::complete("long") 

sexed19_imp1 <- sexed19_imp1_long %>% #separate this to save energy 
  group_by(.imp) %>%
  do(model = glm(formula = cbind(Female, Male) ~ Block +
                   Crop_ID*Corn_weed_management,
                 data=., family=binomial)) %>%
  as.list() %>%
  .[[-1]] %>%
  pool()

sexed19_imp1_eu <- sexed19_imp1_long%>%
  group_by(.imp, Block, Crop_ID, Corn_weed_management) %>%
summarize(Female = sum(Female),
            Male = sum(Male),
            Total = sum(Total)) # 24 data sets, with 72 e.u each. 

#to test the effects of crop identity and corn weed management on sex ratio using 24 imputed data sets 
sexed19_imp1_jt <- sexed19_imp1_eu %>% split(.$.imp) %>% map(mod_jt) 

sexed19_imp1_jt_df <- enframe(sexed19_imp1_jt) %>% #keep "imp" column 
  unnest(cols = c(value)) %>% # everything lines up in order (by imp == name)
rename(.,imp = name) %>%# rename "name" with "imp" for consistency
  mutate(Sig.code = ifelse(p.value < 0.05, "S", "NS")) 

sexed19_imp1_jt_df$imp <- as.numeric(sexed19_imp1_jt_df$imp)
```


```{r, include=FALSE}
sexr_19_panel_names <- c(`Block` = "Block",
                    `Crop_ID` = "Crop ID",
                    `Corn_weed_management` = "Corn weed management",
                    `Crop_ID:Corn_weed_management` = "Crop ID x \n Corn weed management")

## p-values for the effects of crop ID, corn weed management and their interaction from all imputed sets
# stats: shape = 1 for open circles to match with Appendix's mice xyplots
sexr19_imp_p <- ggplot(sexed19_imp1_jt_df, aes(x = imp, y = p.value)) + 
  geom_point(aes(shape=factor(Sig.code),
                 color = factor(Sig.code),
                 size = .5, 
                 alpha = .5)) +  
  facet_wrap(~ `model term`,
             ncol = 2,
             labeller = as_labeller(sexr_19_panel_names))+
  ggtitle("(B) p.values") + 
  geom_hline(yintercept=0.05, size=0.5, linetype = "dashed") + 
  theme_bw() + 
  theme(text=element_text(size=12),
        strip.text = element_text(size = 10))  +
  xlab("Imputation") + 
  ylab("") + 
  scale_color_brewer(palette = "Dark2") +
#  scale_shape_manual(values=1)+
  theme(legend.position = "none",
        panel.spacing = unit(1, "lines"))  +
  scale_size(guide=FALSE)

## F-values for the effects of crop ID, corn weed management and their interaction from all imputed sets
sexr19_imp_F <- ggplot(sexed19_imp1_jt_df , aes(x = imp, y = F.ratio)) + 
   geom_point(aes(shape=factor(Sig.code),
                  color = factor(Sig.code),
                  size = .5, 
                  alpha = .5)) +   #shape = 1) +
  facet_wrap(~ `model term`, 
             ncol = 2, 
             labeller = as_labeller(sexr_19_panel_names)) +
  ggtitle("(C) F.values") + 
  theme_bw() + 
  theme(text=element_text(size=12),
        strip.text = element_text(size = 10))  +
  xlab("Imputation") + 
  ylab("") + 
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none",
        panel.spacing = unit(1, "lines"))  +
  scale_size(guide=FALSE)
```


```{r, include=FALSE}
## Imputed 2019 sex ratio with m = 24 iterations, Jan 29, 2022. The data set on July 16, 2021 is not reproducible as of Jan 29, 2022.  The outcomes from the two data sets are similar.

## This data set is used on the second round of manuscript revision.
sexed19_m24_Jan29 <- read_csv("../2-Data/Clean/sexed19_m24_Jan29_22.csv",
                   col_types = cols(Male = col_integer(), 
                                    Female = col_integer()))

sexed19_m24_Jan29  <- sexed19_m24_Jan29  %<>%
  mutate_at(c("Block","Crop_ID","Corn_weed_management", ".imp"),funs(factor(.)))
sexed19_m24_Jan29$Crop_ID <- factor(sexed19_m24_Jan29$Crop_ID, levels = c("C2", "S2",
                                                                "C3", "S3", "O3",
                                                                "C4", "S4", "O4", "A4")) 

sexed19_m24_Jan29  <- sexed19_m24_Jan29  %>%
  mutate(Rotation = ifelse(Crop_ID %in% c("S2", "C2"), "2-year",
                           ifelse(Crop_ID %in% c("S3", "C3", "O3"), "3-year", "4-year")))


```


```{r sexr19-arrow, echo=FALSE, fig.cap = "Waterhemp population sex ratios under nine crop idenitites averaged over two Corn weed management regimes using 2019's 24 imputed data sets (A). The dashed lines mark sex ratio parity in panel A and level of confidence in panel B, respectively. The blank spaces are nonestimable values. The triangulars and circles in panel A represent female-biased and even populations assessed at alpha = 0.05, respectively. F-values for sources of variation are shown in panel C.", fig.width=8, fig.height=10}


## Means calculated with Crop ID and averaged over Corn weed management regimes

sexed19_imp1_emm_crop_ID <- sexed19_m24_Jan29  %>% split(.$.imp) %>% map(mod_emm_crop_ID) 

## Convert the sexed19_imp1_emm_h dataframe to long format 
sexed19_imp1_emm_long <- do.call(rbind, lapply(sexed19_imp1_emm_crop_ID , as.data.frame))  %>%
  mutate(x = row.names(.))%>%
  mutate(x_num = as.numeric(x),
    imp = floor(x_num),
    Sig.code = ifelse(p.value < 0.05, "S", "NS")) 

## map a ggplot function then patchwork to add blank panels between rotations. <https://patchwork.data-imaginist.com/articles/guides/layout.html>  

sexed19r <- ggplot(sexed19_imp1_emm_long, aes(x = imp, y = prob)) + 
#  geom_point(aes(size = 1, col = Sig.code), shape = 1) +
 geom_point(aes(shape=factor(Sig.code),
                color = factor(Sig.code),
                size = .25,
                alpha = .5)) +   #shape = 1) +
   facet_wrap(~ Crop_ID, ncol = 3)+
  geom_hline(yintercept=0.5, size=0.5, linetype = "dashed") + 
  theme_bw() + 
  theme(text=element_text(size=12))  +
  ggtitle("(A) 2019 sex ratio") +
  xlab("Imputation") + 
  ylab("Female proportion") + 
  scale_color_brewer(palette = "Dark2") +
#   scale_shape_manual(values=1)+
  theme(legend.position = "none",
        panel.spacing = unit(1, "lines"))  +
  scale_size(guide=FALSE)

 sexed19r / (sexr19_imp_p | sexr19_imp_F) 
```


