---
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  #bookdown::word_document2
  bookdown::pdf_document2: 
#    keep_tex: true
    toc: false
    latex_engine: lualatex
    citation_package: natbib
bibliography: fecund.bib
csl: apa-no-ampersand.csl
--- 

```{r, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE, fig.pos ="h")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 16, fig.height = 16,
                      full.fig.width = T, out.width="100%" ,
                     fig.pos = "H", table.placement = "H")
library(emmeans)
library(here)
library(readr)
library(VIM)
library(mice)
library(tidyverse)
library(tidyr)
library(miceadds)
library(data.table)
library(grid); library(gridExtra)
library(kableExtra)
source(here("8 Analysis scripts/functions.R"))
#set.seed(500)
#View(sexed19_mis)
# some pooling stuff here https://bookdown.org/mwheymans/bookmi/rubins-rules.html
RNGkind(sample.kind = "Rounding")
options(digits = 4)
library(patchwork)
library(nlme)
library(broom)
library(broom.mixed)
library(ggResidpanel)
options(scipen=999)
```


## Appendix B: 2019 sex ratio imputation {-}  

### Data set and imputation procedure overview {-}  

The experiment design was RCBD with four blocks, nine levels of main plot (Crop ID) and two levels of split-plot (Corn weed management) effects. There were 72 experiment units (eu), 8 observational units (quadrats) per eu. Within each quadrats, six cohorts of plants were sexed. By the time that the plants were sexed, a few plants' sexes were not observable and thus, they are marked as Unknown in the data set. This caused Total > Male + Female in some eu's. 

Complete case analysis, in which missing observations are removed from the data set, is acceptable when less than 5% of the data is missing at random because removing the incomplete cases does not significantly change the outcome [@azurMultipleImputationChained2011]. The 2019 sex ratio is imputed because 22% of the data (755 `NA`s out of 3448 entries) was missing at random (MAR). We considered our data MAR even though the number of missing values were higher in soybean plots than in the other three crops because 1) the quadrats were placed randomly in the field before weed emergence, 2) waterhemp and other weed seedlings were present in the quadrats at the beginning of the season, and 3) waterhemp and other weed species were found in soybean plots by the time we sexed the waterhemp plants, but not in the eight fixed quadrats.  

The MICE imputation method assumes that after controlling for all the observation in the original data set, all the missingness occurs at random [@vanbuurenMiceMultivariateImputation2011]. A good imputation model is numerically recognized by low fraction of information missing due to nonresponse (`fmi`), small proportion of total variance that is attributable to the missing data ($\lambda$) values; and visually recognized by the similarity in kernel density estimates and data points distribution between the observed and imputed data sets [@vanbuurenMiceMultivariateImputation2011]. The number of imputations (m) should be chosen such that the loss of efficiency, $le = \frac{fmi}{m} \leq 0.05$ [@whiteMultipleImputationUsing2011]. To give the imputation model more information, the data was imputed using 3448 data points. The analysis model on the imputed data sets was run using 72 data points.  

The recommended specifications of the imputation model for this data set are: 1) uses at least 24 imputations (24 was selected because it is divisible by 4 cores in the computer processor), 2) includes all the covariates (Number of emerged seedlings, Male, Female, and Total) and predictors in the analysis model, and 3) uses an overdispersed Poisson regression model [@azurMultipleImputationChained2011; @whiteMultipleImputationUsing2011; and @nguyenModelCheckingMultiple2017]. While the first two specifications were met, overdispersed Poisson regression model could not be specified. The extensions for count data mentioned in Chapter 7 [@vanbuurenFlexibleImputationMissing2018] do not fit this data set well. Both `micemd`'s `mice.impute.2l.glm.pois` and `mice.impute.2l.2stage.pois` functions impute the numbers of Male, Female, and Total separately [@audigierMicemdMultipleImputation2019]. The predictive mean matching (`pmm`) method in the `mice` package can handle counts [@vanbuurenMiceMultivariateImputation2011] and is the optimal solution for this data set at this writing (Figure \@ref(fig:kernel-xy-imp1-all-diag)). 


```{r, echo=FALSE}
sexed19_mis <- read_csv(here("2 Data/Clean data/sexed19_mis.csv"), 
    col_types = cols(Plot = col_factor(), 
        Quadrat = col_factor(), 
        Cohort = col_factor(), 
        Block = col_factor(), 
        Crop = col_factor(),
        Crop_ID = col_factor(),
        Rotation = col_factor(),
         Herbicide = col_factor(),
        Corn_weed_management = col_factor(),
        Number_begin = col_integer(), 
        Total = col_integer(), 
        Female = col_integer(),
        Male = col_integer(), 
        Unknown = col_integer(), 
        Total_sexed = col_integer(), 
        Year = col_character()))

#summary(sexed19_mis)
```

 

```{r, echo=FALSE, warning=F, message=F}
# na.rm= T to remove NA observations from the summary. R will return sums as NA if NA are included in the vector  
sexed19_mis_eu <- sexed19_mis %>% 
  group_by (Plot, Side, Corn_weed_management, Crop_ID, Rotation, Crop, Block, Year) %>%
  summarize(Number_begin = sum(Number_begin, na.rm = T), 
            Total = sum(Total, na.rm = T),
            Female = sum(Female, na.rm = T),
            Male = sum(Male, na.rm = T),
            Total_sexed = sum(Total_sexed, na.rm = T),
            Unknown = sum(Unknown, na.rm = T))
#summary(sexed19_mis_eu)

#str(sexed19_mis_eu)
```

```{r, include=FALSE}

mice_plot1 <- aggr(sexed19_mis[,c(11:14,17)] , col=c('navyblue','yellow'),
                   numbers=TRUE, sortVars=TRUE,
                   labels=names(sexed19_mis[,c(11:14, 17)]), 
                   cex.axis= 1,
                   cex.numbers = .2,
                    ylab=c("Missing data","Pattern"))

mice_plot1 ## data is either NA in all 3 categories, or known, no NA for 2 categories or  1 because Total = F + M + U
```


```{r, echo=F} 
## Categorical, independent variables are included, except quadrats. 
sexed19_resp1 <- sexed19_mis %>% 
  dplyr::select(Block, Crop_ID, Corn_weed_management, Female, Male, Total, Number_begin)

#trial 1, see if lambda and fmi are small, m = 24 = 4 cores x 6 imputations/core
#sexed19_resp1 because categorical variables with no missing cells are included 

sexed19_imp1_wide <- parlmice(sexed19_resp1 , cluster.seed = 500, print = FALSE, n.core = 4, n.imp.core = 6) # to use for visual later, change meth?


sexed19_imp1_long <- sexed19_imp1_wide %>%
  mice::complete("long") 

sexed19_imp1 <- sexed19_imp1_long %>% #separate this to save energy 
  group_by(.imp) %>%
  do(model = glm(formula = cbind(Female, Male) ~ Block + Crop_ID + Corn_weed_management +
                   Crop_ID:Corn_weed_management,
  data=., family=binomial)) %>%
  as.list() %>%
  .[[-1]] %>%
  pool()

```


### Diagnosis of the imputation model with m = 24 {-}

The imputation code with predicted mean matching (`pmm`) method is provided in the Supplementary Material section. Each round of imputation is distinguished by the number of imputation (m). The loss of efficiency (le) are all below the recommended value of 0.05 [@whiteMultipleImputationUsing2011] for the analysis model terms using the imputed data sets, under three m values and the imputation performance improved as m increased (Table \@ref(tab:pool-diag)). m was capped at 2400 imputations for this manuscript because of limited computational power.   
The diagnosis of data imputation is demonstrated here with m = 24 for ease of view. The distribution of the imputed data sets match that of the observation (Figure \@ref(fig:kernel-xy-imp1-all-diag)) so the outputs (imputed data sets) were used for further regression analyses that involved sex ratio. 

### Diagnosis of the analysis model with m = 24 {-}

The similarity in the magnitude of reduction of deviance and dispersion values suggests comparable, small impacts of population aboveground mass and population stand density covariates on the improvement of the goodness of fit for comparing sex ratio using 2019 imputed data (Data Repository). In addition, using either of them as a covariate in the analysis models resulted in nonestimable corn weed management effects on sex ratios in some treatments, so 2019 sex ratios were averaged over corn weed management regimes and compared without any covariates for simplicity. 


```{r imp1-trace, fig.cap= "Convergence diagnosis with m = 24. Each color represents one imputation. The y-axis values are the means and standard deviations of female, male and total plants in each quadrat.", include=FALSE}

plot(sexed19_imp1_wide)
```


```{r, include=FALSE}
dens_all <- densityplot(sexed19_imp1_wide, 
            main = list(label = "A", fontsize = 20), 
            xlab = list(lable = "Density", fontsize = 20),
                   scales=list(tck=c(1,0), x=list(cex=2), y=list(cex=2)))

#every factors in the imputation model go in the glm model 
fit1 <- with(sexed19_imp1_wide, glm(ici(sexed19_imp1_wide) ~ Male + Female + Total + Number_begin + Crop_ID + Corn_weed_management + Crop_ID:Corn_weed_management + 
                                      Block,
                     family = binomial))
ps1 <- rep(rowMeans(sapply(fit1$analyses, fitted.values)),
          sexed19_imp1_wide$m + 1)

#<https://stefvanbuuren.name/fimd/sec-diagnostics.html>

xy_female <- xyplot(sexed19_imp1_wide, Female ~ ps1 | as.factor(.imp),
       main = list(label = "(A)", fontsize = 20),
       xlab = list(label = "Probability that record is incomplete", fontsize = 20),
       ylab = list(label = "Female", fontsize = 20),
       pch = c(15, 16), col = mdc(1:2),
              scales=list(tck=c(1,0), x=list(cex=2), y=list(cex=2)))

xy_male <-  xyplot(sexed19_imp1_wide, Male ~ ps1 | as.factor(.imp),
       main = list(label = "(B)", fontsize = 20),
       xlab = list(label = "Probability that record is incomplete", fontsize = 20),
       ylab = list(label="Male", fontsize=20) , 
       pch = c(15, 16), col = mdc(1:2),
       scales=list(tck=c(1,0), x=list(cex=2), y=list(cex=2)))
```


```{r kernel-xy-imp1-all-diag, fig.cap="Number of female (A) and male (B) against the missingness probability for observed (data set numbered 0) and imputed data (data set numbered 1 to 24).", echo=F}

grid.arrange( xy_female, xy_male) #patchwork doesn't accommodate lattice
```


```{r jt1-pool, echo=FALSE, message=F, warning=F}

sexed19_imp1_eu <- sexed19_imp1_long%>%
  group_by(.imp, Block, Crop_ID, Corn_weed_management) %>%
summarize(Female = sum(Female),
            Male = sum(Male),
            Total = sum(Total)) # 24 data sets, with 72 e.u each. 

#write.csv(sexed19_imp1_eu, here("2 Data/Clean data/sexed19_m24.csv"),row.names = F)

sexed19_imp1_jt <- sexed19_imp1_eu %>% split(.$.imp) %>% map(mod_jt) 

sexed19_imp1_jt_df <- enframe(sexed19_imp1_jt) %>% #have imp kept
  unnest(cols = c(value)) %>% # everything lines up in order (by imp == name)
rename(.,imp = name) # rename "name" with "imp" for consistency

sexed19_imp1_full <- sexed19_imp1_jt_df %>% 
  filter(is.na(note)) 

sexed19_imp1_notfull <-  sexed19_imp1_jt_df %>% 
  filter(!is.na(note))

n_imp1_notfull <- sexed19_imp1_notfull %>%  
distinct(imp)%>% tally() #give the number of df 

n1 <- nrow(sexed19_imp1_full)/4

```

```{r, include=F}
#for demo purpose
#imp1_full <- sexed19_imp1_eu %>% filter(.imp == 6)

#write.csv(imp1_full, here("2 Data/Clean data/sexed19.csv"),row.names = F)

```



```{r m240, echo=FALSE , message=F, warning=F}
#trial 2, see if lambda and fmi are smaller, m = 240 = 4 cores x 60 imputations/core

sexed19_imp2_wide <- parlmice(sexed19_resp1 , cluster.seed = 500, print = FALSE, n.core = 4, n.imp.core = 60) # to use for visual later, change meth?

sexed19_imp2_long <- sexed19_imp2_wide %>%
  mice::complete("long") 

sexed19_imp2 <- sexed19_imp2_long %>% #separate this to save energy 
  group_by(.imp) %>%
  do(model = glm(formula = cbind(Female, Male) ~ Block + Crop_ID + Corn_weed_management +
                   Crop_ID:Corn_weed_management,
  data=., family=binomial)) %>%
  as.list() %>%
  .[[-1]] %>%
  pool()

```
```{r m240-jt, echo=F, message=F, warning=F}
## check for number of full sets
sexed19_imp2_eu <- sexed19_imp2_long%>%
  mutate(Year = "2019",
    Rotation = ifelse(Crop_ID %in% c("S2", "C2"), "2-year",
                           ifelse(Crop_ID %in% c("S3", "C3", "O3"), "3-year", "4-year")))%>%
  group_by(.imp, Block, Crop_ID, Corn_weed_management, Rotation, Year) %>%
summarize(Female = sum(Female),
            Male = sum(Male),
            Total = sum(Total)) 

sexed19_imp2_jt <- sexed19_imp2_eu %>% split(.$.imp) %>% map(mod_jt) 

sexed19_imp2_jt_df <- enframe(sexed19_imp2_jt) %>% #have imp kept
  unnest(cols = c(value)) %>% # everything lines up in order (by imp == name)
rename(.,imp = name) # rename "name" with "imp" for consistency

#on a Mac, m = 240 gives 1 full set, numbered 9
sexed19_imp2_full <- sexed19_imp2_jt_df %>% 
  filter(is.na(note)) 

n2 <- nrow(sexed19_imp2_full)/4 #28
```

```{r m2400, echo=FALSE, message=F, warning=F}
#trial 2, see if lambda and fmi are smaller, m = 2400 = 4 cores x 600 imputations/core

sexed19_imp3_wide <- parlmice(sexed19_resp1 , cluster.seed = 500, print = FALSE, n.core = 4, n.imp.core = 600) # to use for visual later, change meth?

sexed19_imp3_long <- sexed19_imp3_wide %>%
  mice::complete("long") 

sexed19_imp3 <- sexed19_imp3_long %>% #separate this to save energy 
  group_by(.imp) %>%
  do(model = glm(formula = cbind(Female, Male) ~ Block + Crop_ID + Corn_weed_management +
                   Crop_ID:Corn_weed_management,
  data=., family=binomial)) %>%
  as.list() %>%
  .[[-1]] %>%
  pool()

```

```{r m2400-jt, echo=FALSE , message=F, warning=F}

## check for number of full sets
sexed19_imp3_eu <- sexed19_imp3_long%>%
  mutate(Year = "2019",
    Rotation = ifelse(Crop_ID %in% c("S2", "C2"), "2-year",
                           ifelse(Crop_ID %in% c("S3", "C3", "O3"), "3-year", "4-year")))%>%
  group_by(.imp, Block, Crop_ID, Corn_weed_management, Rotation, Year) %>%
summarize(Female = sum(Female),
            Male = sum(Male),
            Total = sum(Total)) 

sexed19_imp3_jt <- sexed19_imp3_eu %>% split(.$.imp) %>% map(mod_jt) 

sexed19_imp3_jt_df <- enframe(sexed19_imp3_jt) %>% #have imp kept
  unnest(cols = c(value)) %>% # everything lines up in order (by imp == name)
rename(.,imp = name) # rename "name" with "imp" for consistency

#on a Mac, m = 240 gives 1 full set, numbered 9
sexed19_imp3_full <- sexed19_imp3_jt_df %>% 
  filter(is.na(note)) 

sexed19_imp3_not_full <- sexed19_imp3_jt_df %>% 
  filter(!is.na(note)) # nrow = 6168, n sets = 6168/3 = 2056

n3 <- nrow(sexed19_imp3_full)/4 #344; 344 + 2056 = 2400


```

```{r pool-diag, echo=F}
#combine all scenarios of m, column-wise  
#<https://rdrr.io/cran/mice/man/cbind.mids.html>

n <- c(rep(n1,21), rep(n2,21), rep(n3,21))

all_imp <- rbind(sexed19_imp1$pooled, sexed19_imp2$pooled, sexed19_imp3$pooled) 

all_imp_n <- cbind(all_imp, n) %>%
  mutate(le = fmi/m,
         `n/m` = n/m) %>%   # le = loss of efficiency , prop_full = % of fully imputed data sets. 
dplyr::select(term, m, `n/m`, riv, fmi, lambda, le)

all_imp_wide <- cbind(all_imp_n[1:21,], all_imp_n[22:42,], all_imp_n[43:63,])


all_imp_n_ordered <- all_imp_n[order(all_imp_n$term),]

all_imp_n_ordered_wide <- all_imp_n_ordered %>% 
  pivot_wider(names_from = m, values_from = c(`n/m`, riv, fmi, lambda, le)) %>%
  setNames(gsub(".*_","m = ",names(.)))

all_imp_n_ordered_wide$term <- gsub(":", " x ", all_imp_n_ordered_wide$term)
all_imp_n_ordered_wide$term <- gsub("_", " ", all_imp_n_ordered_wide$term)
all_imp_n_ordered_wide$term <- gsub("corn", "Corn", all_imp_n_ordered_wide$term)
all_imp_n_ordered_wide$term <- gsub("ID", "ID: ", all_imp_n_ordered_wide$term)
all_imp_n_ordered_wide$term <- gsub("cide", "cide: ", all_imp_n_ordered_wide$term)
all_imp_n_ordered_wide$term <- gsub("Block", "Block: ", all_imp_n_ordered_wide$term)
all_imp_n_ordered_wide$term <- gsub("(Intercept)", "Intercept", all_imp_n_ordered_wide$term)

kbl(all_imp_n_ordered_wide, booktabs = T, linesep = "",
    caption = "Imputation model indices with different values of m. NAs resulted from nonestimable number of male and female in a treatment.") %>%
  add_header_above(c(" " = 1, 
                     "n/m" = 3, 
                     "riv" = 3,
                     "fmi" = 3,
                     "lambda" = 3,
                     "le" = 3), border_left = F, border_right = F) %>%
  column_spec(c(4,7,10,13,16), border_left = F, border_right = F) %>%
  kable_styling(latex_options = c( "scale_down")) %>%
  landscape()
  

#all_imp_long <- pivot_longer(all_imp_n, !c(term, m), names_to = "index")

#View(all_imp_long)
#fig.cap= "Visualization of  The model terms are listed (left to right) from intercept to interactions."
#ggplot(all_imp_long, aes(x = term, y = value)) + 
#  geom_jitter(aes(col = as.factor(m), size = 2)) + 
#  facet_wrap(~index, ncol = 2, scales = "free_y") +
#  theme_bw() + 
#  theme( #axis.text.x = element_blank(),
#        legend.position = c(0.7, 0.12)) +
#  theme(text=element_text(size=25))  +
#  theme(legend.title = element_blank()) +
#  xlab("Analysis model term") + 
#  ylab("Parameter value") + 
#  scale_color_brewer(palette = "Set1") +
#  scale_size(guide=FALSE)
```
   

```{r, include=FALSE, warning=FALSE, message=FALSE}
library(purrr)
library(magrittr)
sexed18 <- read_csv("../2 Data/Clean data/sexed18.csv", 
                    col_types = cols(Male = col_integer(), 
                                     Female = col_integer()))

sexed18 <- sexed18  %<>%
  mutate_at(c("Block","Crop_ID","Rotation","Corn_weed_management", "Plot", "Side", "Year"),funs(factor(.)))

#sexed18[is.na(sexed18)] <- 0 #NA replaced with 0


sexed18$Crop_ID <- factor(sexed18$Crop_ID, levels = c("C2", "S2",
                                                                "C3", "S3", "O3",
                                                                "C4", "S4", "O4", "A4"))

sexed18.glm <- glm(cbind(Female, Male) ~ Block + Crop_ID + Corn_weed_management + Crop_ID:Corn_weed_management,
  data=sexed18, family=quasibinomial(link = "logit"))
#fig.cap="Diagnosis plot for a model of population sex ratio as a function of the experimental factors and population above-ground mass covariate. Deviance = 165.91."
#anova(sexed18.glm, test="F")
```

```{r, include=FALSE}
sexed18.emm <- emmeans(sexed18.glm, c("Crop_ID", "Corn_weed_management"), type = "response")

plot(sexed18.emm, by = "Corn_weed_management", comparisons = T) + coord_flip() + theme_bw()
```



```{r, include=FALSE}
sexed19_m24 <- sexed19_imp1_eu

sexed19_m24 <- sexed19_m24  %<>%
  mutate_at(c("Block","Crop_ID","Corn_weed_management", ".imp"),funs(factor(.)))
sexed19_m24$Crop_ID <- factor(sexed19_m24$Crop_ID, levels = c("C2", "S2",
                                                                "C3", "S3", "O3",
                                                                "C4", "S4", "O4", "A4")) 

sexed19_m24 <- sexed19_m24 %>%
  mutate(Rotation = ifelse(Crop_ID %in% c("S2", "C2"), "2-year",
                           ifelse(Crop_ID %in% c("S3", "C3", "O3"), "3-year", "4-year")))
```


```{r, include=FALSE}  
sexed19_imp1_summ <- sexed19_m24 %>% split(.$.imp) %>% map(mod_sum) 

sexed19_imp1_summ_df <- enframe(sexed19_imp1_summ) %>% 
  unnest(cols = c(value)) %>%
  mutate(name = as.factor(name)) %>%
  dplyr::rename(, Imputation = name) %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))

```

```{r sexr19-covar-summ, echo=FALSE}
amata19 <- read_csv("../2 Data/Clean data/AMATA_19.csv",
                    col_types = cols(Plot = col_factor(), 
                                     Block = col_factor(), 
                                     Crop = col_factor(),
                                     Crop_ID = col_factor(),
                                     Corn_weed_management = col_factor(),
                                     Year = col_character()))

amata19$Crop_ID <- factor(amata19$Crop_ID, levels = c("C2", "S2",
                                                                "C3", "S3", "O3",
                                                                "C4", "S4", "O4", "A4"))
prop_biom19 <- amata19 %>% left_join(sexed19_m24)

sexr19_biom_imp1_summ <- prop_biom19 %>% split(.$.imp) %>% map(sexr19_biom_sum) 

sexr19_biom_imp1_summ_df <- enframe(sexr19_biom_imp1_summ) %>% 
  unnest(cols = c(value)) %>%
  mutate(across(where(is.numeric), ~ round(., 2))) %>%
  mutate(name = as.factor(name)) %>%
  dplyr::rename(, Imputation = name) 
   #numerical diagnosis with population biomass covar


sexr19_dens_imp1_summ <- prop_biom19 %>% split(.$.imp) %>% map(sexr19_dens_sum) 

sexr19_dens_imp1_summ_df <- enframe(sexr19_dens_imp1_summ) %>% 
  unnest(cols = c(value)) %>%
  mutate(name = as.factor(name)) %>%
  dplyr::rename(, Imputation = name) %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))

imp_orginal <- rbind(t(sexr19_biom_imp1_summ_df),
      t(sexr19_dens_imp1_summ_df), 
      t(sexed19_imp1_summ_df)) 


kbl(imp_orginal, booktabs = T, 
    caption = "Numerical diagnosis of model's goodness of fit with and without covariates on 2019 imputed data sets.") %>%
  pack_rows("(A) Population aboveground mass covariate", 1,3) %>% 
  pack_rows("(B) Population stand density covariate", 4,6) %>%
  pack_rows("(C) No covariate", 7,9)  %>% 
  kable_styling(latex_options =  c("scale_down")) %>%
  landscape()
```

```{r, include=FALSE}
fecundity18 <- read_csv(here("2 Data/Clean data/fecundity_18.csv"), 
    col_types = cols(Biomass = col_number(), 
        Seed = col_number()), na = "empty")

fecundity18$Crop_ID <- factor(fecundity18$Crop_ID, levels = c("C2", "S2",
                                                                "C3", "S3", "O3",
                                                                "C4", "S4", "O4", "A4"))

fecundity18$label <- paste(as.character(fecundity18$Rotation), "year", sep="-")

fecundity18  <- fecundity18   %<>%
  mutate_at(c("Block","Crop_ID","Rotation","Corn_weed_management", "Plot", "Side", "bt"),funs(factor(.)))

fecundity18_b <- fecundity18[complete.cases(fecundity18$Biomass), ]
min(fecundity18_b$Biomass[fecundity18_b$Biomass > 0])
```

```{r, include=FALSE}
sexed18 <- read_csv("../2 Data/Clean data/sexed18.csv", 
                    col_types = cols(Male = col_integer(), 
                                     Female = col_integer()))

sexed18 <- sexed18  %<>%
  mutate_at(c("Block","Crop_ID","Rotation","Corn_weed_management", "Plot", "Side", "Year"),funs(factor(.)))

sexed18[is.na(sexed18)] <- 0 #NA replaced with 0


sexed18$Crop_ID <- factor(sexed18$Crop_ID, levels = c("C2", "S2",
                                                                "C3", "S3", "O3",
                                                                "C4", "S4", "O4", "A4"))


sexed18.glm <- glm(cbind(Female, Male) ~ Block + Crop_ID + Corn_weed_management  + Crop_ID:Corn_weed_management ,
  data=sexed18, family=quasibinomial(link = "logit"))

# every models before arriving at this models are at 'sexr ANCOVA trials.Rmd'
#min(prop_biom18$g_m_sq[prop_biom18$g_m_sq > 0])
prop_biom18 <- read_csv("../2 Data/Clean data/f_prop_biom18.csv",
                    col_types = cols(Plot = col_factor(), 
                                     Block = col_factor(), 
                                     Crop = col_factor(),
                                     Crop_ID = col_factor(),
                                     Corn_weed_management = col_factor(),
                                     Year = col_character()))

sexr18_biom_glm3 <- glm(cbind(Female, Male) ~ Block +  Crop_ID + Corn_weed_management + 
                          log(g_m_sq + 0.00025) +
                        Crop_ID:Corn_weed_management + 
                        log(g_m_sq + 0.00025):Crop_ID +
                        log(g_m_sq + 0.00025):Corn_weed_management +
                        log(g_m_sq + 0.00025):Crop_ID:Corn_weed_management ,
  data=prop_biom18, family=quasibinomial(link = "logit"))


sexr18_dens_glm3 <- glm(cbind(Female, Male) ~ Block  + Crop_ID + Corn_weed_management +
                          + log(plant_m_sq + 0.025)  +
                        Crop_ID:Corn_weed_management + 
                        log(plant_m_sq + 0.025):Crop_ID +
                        log(plant_m_sq + 0.025):Corn_weed_management +
                        log(plant_m_sq + 0.025):Crop_ID:Corn_weed_management ,
  data=prop_biom18, family=quasibinomial(link = "logit"))

#<http://web.pdx.edu/~newsomj/cdaclass/ho_glm.pdf>
```

```{r sexr18-covar-diag, include = F}
num_diag_sexed18 <- data.frame(imp = "None",
                          Deviance = summary(sexed18.glm)$deviance,
                          Dispersion = summary(sexed18.glm)$dispersion)%>% 
  mutate(across(where(is.numeric), ~ round(., 2)))

num_diag_sexr18_biom <- data.frame(imp = "None",
                          Deviance = summary(sexr18_biom_glm3)$deviance,
                          Dispersion = summary(sexr18_biom_glm3)$dispersion) %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))

num_diag_sexr18_dens <- data.frame(imp = "None",
                          Deviance = summary(sexr18_dens_glm3)$deviance,
                          Dispersion = summary(sexr18_dens_glm3)$dispersion) %>% 
  mutate(across(where(is.numeric), ~ round(., 2)))

sexr18_covar_diag <- t(rbind(num_diag_sexr18_biom, num_diag_sexr18_dens, num_diag_sexed18)) 

sexr18_covar_diag %>%
  kbl(longtable = F, booktabs = T, linesep = "",
    caption = "Numerical diagnosis of model's goodness of fit with versus without covariates on 2018 data set") %>%
   add_header_above(c(" " = 1,
                      "Population aboveground mass added" = 1, 
                      "Population stand density added" = 1,
                      "No covariate" = 1)) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  landscape()
```

