---
title: "Impact of cropping system diversification on vegetative and reproductive characteristics of waterhemp (*Amaranthus tuberculatus*)"
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output:
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
    number_sections: false
    extra_dependencies: ["float"]
    latex_engine: lualatex
    citation_package: natbib
bibliography: fecund.bib
natbiboptions: round
biblatexoptions:
  - sortcites = true
  - sorting = nyt
  - backend = biber
  - maxcitenames = 2
csl: apa-no-ampersand.csl
---
*This script demonstrates how the sections were put together before final processing with Overleaf. Some typos and raw LaTeX codes may present.*

# Abstract {-}

```{r, child = "Abstract.Rmd"}
```

# Introduction {-}

```{r, child = "Introduction.Rmd"}
```

# Materials and Methods {-}

```{r, child = "Proposal.Rmd"}
```


# Results {-}

Using `ggResidpanel` version 0.3.0 for model diagnosis [@goodeGgResidpanelPanelsInteractive2019], no predictable pattern in the plots of residuals versus predicted values suggests that the analysis models fit the data well (Details are provided in @nguyenDataImpactCropping2022).  
In all rotations, all the crop yields were comparable to those of Iowa and Boone County (where the experiment is situated) [@nguyenWeedCommunityCompositioninpreparation].  


```{r, child = "../5 Analysis/Individual-fecundity-model.Rmd" }
# knitting this chunk and the next produced raw Latex code because of some package conflicts - not resolved yet
```


```{r, child = "../5 Analysis/Population-sex-biom-dens.Rmd"}
```


# Discussion {-}

```{r, child = "Discussion.Rmd"}
```

# Appendix {-}

```{r, child = "AppendixA.Rmd"}
#seed cleaning and counting procedure
```


```{r, child = "../4 Data wrangling/sex-19-imputation.Rmd"}
# This is Appendix B
```

# Acknowledgements {-}
The authors thank Matt Woods, Mike Fiscus, and the Iowa State University’s Agronomy Research Farm crew for field management; Jessica Juarez-Morales, Elizabeth Oys, Ana Poznanski, Andrew Riehl, Angela Soto-Saenz, and Wyatt Westfall for field and laboratory assistance; Alan Gaul and Iowa State University’s Seed Laboratory student assistants and interns for seed cleaning laboratory space, guidance, and technical assistance; Philip Dixon and Dean Adams for data analysis assistance; Russ Lenth and other Stackoverflow community members for answering HN's coding questions; and Lisa Schulte-Moore, Micheal Owen, and Mark Gleason for reviewing the manuscript.  

# References {-}
